Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-13 talk/pepm2011/paper.tex
improve benchmark section

For the former we counted the occurring operations in all generated traces
before and after the optimization phase for all benchmarks. The results can be
seen in Figure~\ref{fig:numops}. The optimization removes as many as XXX and as
little as XXX percent of allocation operations in the traces of the benchmarks.
All benchmarks taken together, the optimization removes XXX percent of
allocation operations.

@@

In addition to the count of operations we also performed time measurements. The
machine the benchmarks were run on is XXX. We compared the performance of
various Python implementations on the benchmarks. As a baseline, we used the
standard Python implementation in C, called
CPython\footnote{\texttt{http://python.org}}, which uses a bytecode-based
interpreter. Furthermore we compared against Psyco \cite{rigo_representation-based_2004}, an extension to
CPython which is a just-in-time compiler that produces machine code at run-time.
It is not based on traces. Finally, we used three versions of PyPy's Python interpreter:
one without a JIT, one including the JIT but not using the allocation removal
optimization, and one using the allocation removal optimizations.

All benchmarks were run 50 times in the same process, to give the JIT time to produce machine
code. The arithmetic mean of the times of the last 30 runs were used as the
result. The errors were computed using a confidence interval with a 95\%
confidence level \cite{georges_statistically_2007}. The results are reported in Figure~\ref{fig:times}.
With the optimization turned on, PyPy's Python interpreter outperforms CPython
in all benchmarks except spambayes (which heavily relies on regular expression
performance). All benchmarks are improved by the allocation removal
optimization, some as much as XXX. XXX Psyco

>>>>

The benchmarks were run on an otherwise idle Intel Core2 Duo P8400 processor
with 2.26 GHz and 3072 KB of cache on a machine with 3GB RAM running Linux
2.6.35. We compared the performance of various Python implementations on the
benchmarks. As a baseline, we used the standard Python implementation in C,
CPython 2.6.6\footnote{\texttt{http://python.org}}, which uses a bytecode-based
interpreter. Furthermore we compared against Psyco 1.6
\cite{rigo_representation-based_2004}, an extension to CPython which is a
just-in-time compiler that produces machine code at run-time. It is not based
on traces. Finally, we used two versions of PyPy's Python interpreter (revision
77823 of SVN trunk\footnote{\texttt{https://codespeak.net/svn/pypy/trunk}}): one
including the JIT but not optimizing the traces, and one using the allocation
removal optimizations (as well as some minor other optimizations, such as
constant folding).

As the first step, we counted the occurring operations in all generated traces
before and after the optimization phase for all benchmarks. The resulting
numbers can be
seen in Figure~\ref{fig:numops}. The optimization removes as many as 90\% and as
little as 4\% percent of allocation operations in the traces of the benchmarks.
All benchmarks taken together, the optimization removes 70\% percent of
allocation operations. The numbers look similar for reading and writing of
attributes. There are even more \lstinline{guard} operations that are removed,
however there is an additional optimization that removes guards, so not all the
removed guards are an effect of the optimization described here.

@@

In addition to the count of operations we also performed time measurements.
All benchmarks were run 50 times in the same process, to give the JIT time to produce machine
code. The arithmetic mean of the times of the last 30 runs were used as the
result. The errors were computed using a confidence interval with a 95\%
confidence level \cite{georges_statistically_2007}. The results are reported in Figure~\ref{fig:times}.
With the optimization turned on, PyPy's Python interpreter outperforms CPython
in all benchmarks except spambayes (which heavily relies on regular expression
performance XXX). All benchmarks are improved by the allocation removal
optimization, some as much as XXX. XXX Psyco
